\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}  % Style options: 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}     % Color options: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

\usepackage[scale=0.75]{geometry}

% Personal Information
\name{Ivan}{Evdokimov}
\email{ivevdm@gmail.com}
\phone[*]{+44 7586 774312}

% Custom Variables
\newcommand{\positionname}{Python Developer}
\newcommand{\companyfull}{ JP Morgan Chase }
\newcommand{\companyshort}{JP Morgan Chase}

\begin{document}

% Cover Letter Header
\recipient{}{}
\date{\today}
\opening{Dear Hiring Manager,}
\closing{Kind regards,}

\makelettertitle

I am writing to apply for the Python Developer role at Monzo. I hold a PhD in Computational Finance and have hands-on experience building and running ML systems in regulated, data-heavy environments. I am excited about the chance to help your company deliver reliable and highly scalable AI solutions.

In my current role as a Software Engineer at the University of Essex, I build AI systems that use large language models together with cloud data pipelines to automate business data collection and validation. The range of projects includes LLM-based data extraction and checking, as well as fully automated CI/CD pipelines which allow clients to deploy their solutions in a safe and repeatable way. Before this, at the UK Data Service, I built Python and JavaScript applications integrating and fine-tuning LLMs (with vLLM and Ollama) to automate metadata processing, disclosure-risk checks and data quality control for sensitive research data. These tools helped non-technical users work faster while still meeting strict security and governance rules.

My academic background also fits this role well. During my PhD in Computational Finance, I built a transfer-learning-based Bayesian Model Averaging system to forecast financial variables, published papers in international computer science journals, and released open-source software that other developers now use. I am comfortable moving from research and testing into building stable, production-ready systems.

Alongside my professional work, I built and deployed a personal OCR project for Magic: The Gathering cards that is used by around 50 users per day. The system runs on a Raspberry Pi and uses Python and C++ to scan card images, recognize text, and match it against a PostgreSQL database to return live market prices through a web interface built in JavaScript using Vite and React. This project gave me hands-on experience with end-to-end Computer Vision development, from data processing to deployment on real hardware.

I am especially interested in this role because it covers the full process: from getting and exploring data, to building models, writing software and deploying it in the cloud. My experience with LLMs, NLP, C++, Python and AWS has prepared me to work closely with both technical and business teams and to deliver AI systems that solve real problems.

% JPMorgan’s focus on safe, well-governed AI matches my own experience working with sensitive data and controlled analytics. I would be very happy to bring my skills in applied AI, financial modelling and software engineering to your Corporate Functions team.
%
Thank you for your time and consideration. I look forward to the opportunity to discuss my application.


% I am writing to express my strong interest in the \positionname~role at \companyshort. With a PhD in Computational Finance (University of Essex, 2025) and extensive experience in AI systems and other types of data-intensive applications, I bring advanced modeling and software engineering skills aligned with the interdisciplinary demands of this role.
%
% As part of my PhD, I explored and applied machine learning algorithms and data analytics to predict the earnings per share data of US companies. My analysis and modeling results were presented at international computer science conferences and in journals. I also built Java-based data pipelines and an API to retrieve financial data from the Securities and Exchange Commission website, storing it in my local PostgreSQL server. This data is then used as the input to the ML forecasting system that I designed. Currently, I am finalizing a web application that predicts US stock earnings using my PhD research system, with Python, Java, JavaScipt, and SQL.
%
% As a Data Engineer at the UK Data Service, I developed AI systems for individual household disclosure risk analysis using Python (PyTorch, Hugging Face, scikit-learn). I created and maintained pipelines for data collection, preprocessing, and standardization. In my team, I was also held responsible for coding, testing, and debugging AI prototypes to ensure robust and efficient performance. This gave me experience building UIs in TypeScript/React and integrating APIs for user authorization and AWS. Additionally, I monitored and enhanced the Model Context Protocol Application based on the performance metrics and feedback loops obtained from the data curation team.
%
% I bring a collaborative mindset, having led seminars on ML in finance, pair-programmed on projects from GANs to genetic algorithms, and contributed to macroeconomic simulation research. I enjoy working across disciplines and believe collaboration is critical to creating a better future. As an individual with a keen interest in the financial services industry and investments, I believe that timely and reliable data delivery, paired with user-friendly analytical tools, is what helps make wise investments.
%
% Thank you for considering my application. I would welcome the chance to discuss how my skills can help empower \companyshort's clients with critical insights and intelligence to identify opportunities using thorough data analysis and modelling. I am available at your convenience and look forward to speaking with you.

\vspace{0.25cm}
Kind regards,

Ivan Evdokimov
\end{document}

