\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{xcolor}

% Formatting
\titleformat{\section}{\large\bfseries\color{black}}{}{0em}{}
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[ -- ]
\renewcommand{\familydefault}{\sfdefault}
\pagenumbering{gobble}

\begin{document}

\begin{center}
  \textbf{\Large Ivan Evdokimov} \\[0.2em]
  London, UK \quad $\vert$ \quad ivevdm@gmail.com \\
  \href{https://www.linkedin.com/in/ivan-evdokimov}{linkedin.com/in/ivan-evdokimov} \quad $\vert$ \quad \href{https://github.com/ivan020}{github.com/ivan020}
\end{center}

\section*{Profile}
Computational Finance PhD with strong expertise in machine learning, time series analysis, and stochastic optimisation for financial modelling. Experience in development and deployment of AI models. Proven ability to work across academia and industry, and to translate cutting-edge research into robust commercial applications.

\section*{Education}
\textbf{University of Essex} \hfill 2021 -- 2025 (expected)\\
PhD, Computational Finance\\
\textit{Research: Estimating future earnings per share and free cash flows using statistical and machine learning methods.}

\textbf{University of Essex} \hfill 2020 -- 2021\\
MSc, Financial Econometrics\\
\textit{Focus: Time series modelling, financial risk analysis, econometric forecasting.}

\textbf{Hult International Business School} \hfill 2018 -- 2020\\
Master in Finance\\
\textit{Focus: Asset pricing, financial markets, portfolio management.}

\section*{Experience}
\textbf{UK Data Archive} -- Data Engineer (Part-time) \hfill Jan 2023 -- Present\\
\begin{itemize}[leftmargin=*]
  \item Designed AI-driven solutions (ML, LLM) for Named entry recognition.
  \item Deployment of these solutions to AWS, using Lambda, Step-Functions, EFS.
  \item Applied Python and TDD practices to manage data pipelines.
\end{itemize}

\textbf{University of Essex} -- Research Officer \hfill Oct 2022 -- Dec 2022\\
\begin{itemize}[leftmargin=*]
  \item Developed Python-based macroeconomic models to simulate financial indicators.
  \item Created publication-quality visual outputs for econometric studies.
  \item Gained experience in statistical forecasting and econometric simulations.
\end{itemize}

% textbf{University of Essex} -- Laboratory Assistant \hfill Jan 2022 -- Apr 2022\\
% begin{itemize}[leftmargin=*]
  % item Guided students in security algorithms and low-level systems programming (C/C++).
  % item Delivered educational support in structured computing environments.
% end{itemize}

\textbf{Beyond Borders Investment Strategies} -- Investment Analyst Intern \hfill May 2020 -- Sep 2020\\
\begin{itemize}[leftmargin=*]
  \item Conducted multi-country quantitative and qualitative analysis of impact analysis for risk-informed decisions.
  \item Supported currency exposure modelling under pandemic conditions.
\end{itemize}

\textbf{dczd.tech} -- Analyst Intern \hfill May 2019 -- Jul 2019\\
\begin{itemize}[leftmargin=*]
  \item Performed R\&D financial forecasts and cost modelling for tech ventures.
  \item Delivered trend analysis and business insights for blockchain segment.
\end{itemize}

\textbf{Briteside Marketing Management} -- Associate Analyst \hfill Sep 2015 -- Jul 2018\\
\begin{itemize}[leftmargin=*]
  \item Created dynamic financial models and cash flow projections for multinational clients.
  \item Communicated complex financial scenarios to stakeholders with clarity.
\end{itemize}

\section*{Technical Skills}
\textbf{Languages:} Python, C, C++, SQL, Golang, JavaScript\\
\textbf{ML/AI:} Random Forest, Gradient Boosting, LSTM, RNNs, Stochastic Programming\\
\textbf{Other:} Git, TDD, Agile, risk mitigation modelling

\section*{Publications \\ \small (in progress)}
% Co-authoring peer-reviewed articles on ML-based FX forecasting, stochastic currency hedging, and AI-driven ALM models with the University of Essex.
Evdokimov, I., Kampouridis, M., Papastylianou, T., "Application Of Machine Learning Algorithms to Free Cash Flows Growth Rate Estimation", International Neural Network Society Workshop on Deep Learning Innovations and Applications (INNS DLIA), Procedia Computer Science, Elsevier (2023).

\end{document}

