\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}  % Style options: 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}     % Color options: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

\usepackage[scale=0.75]{geometry}

% Personal Information
\name{Ivan}{Evdokimov}
\email{ie20391@essex.ac.uk}
\phone[*]{+44 7586 774312}

% Custom Variables
\newcommand{\positionname}{Data Scientist --- Volume Forecasting (VF)}
\newcommand{\companyfull}{ EDF Ltd.}
\newcommand{\companyshort}{EDF}

\begin{document}

% Cover Letter Header
\recipient{Hiring Manager}{\companyfull \\ 80 Victoria Street\\ London, SW1E 5JL}
\date{\today}
\opening{Dear Hiring Manager,}
\closing{Kind regards,}

\makelettertitle

I am writing to express my strong interest in the Data Scientist role within the Volume Forecasting Systems team at \companyshort. With a PhD in Computational Finance (University of Essex, 2025) and extensive experience developing time-series forecasting systems in both academic and commercial settings, I bring a blend of advanced modeling expertise and robust software engineering skills that aligns closely with the interdisciplinary demands of this position.

My doctoral research focuses on forecasting fundamental stock metrics --- such as earnings per share and free cash flows --- using statistical and machine learning techniques, including autoregressive models, LSTMs, and tree-based ensembles.
While my background is rooted in financial modeling, the core challenge of understanding and predicting complex, dynamic systems is highly transferable to energy forecasting.
My experience working with heterogeneous, high-frequency and quarterly data and stochastic processes positions me well to contribute meaningfully to \companyshort’s forecasting objectives.

In my role as a Data Engineer at the UK Data Archive, I designed and deployed a hierarchical machine learning pipeline that integrates NLP classification with cloud infrastructure. The pipeline --- built using tree-based models, LSTMs, and feed-forward networks --- was deployed on AWS, automating manual processes and enabling efficient handling of large-scale datasets. I understand that \companyshort is transitioning to a Python-based AWS environment, and I am confident that my experience designing and managing such pipelines will be immediately applicable.

I also bring a strong collaborative mindset, having led seminars on ML applications in finance, pair-programmed with researchers on diverse machine learning projects, ranging from GANs to non-linear estimation with genetic algorithms, and contributed to academic work on macroeconomic simulation. I enjoy working across disciplines and believe that this collaborative approach is critical to succeeding in environments like \companyshort’s, where data science intersects with energy operations and market dynamics.

Although I have not yet worked directly in the energy sector, I am highly motivated by EDF’s mission to help Britain achieve Net Zero. I am eager to apply my forecasting expertise to problems with real-world impact, such as optimizing volume predictions and supporting the transition to a low-carbon future.
Thank you for considering my application. I would welcome the opportunity to further discuss how my experience in forecasting and cloud-based machine learning can support EDF’s innovative work in energy systems. I am available at your convenience and look forward to the opportunity to speak with you.

\vspace{0.25cm}
Kind regards,

Ivan Evdokimov
\end{document}

