\documentclass[11pt]{letter}

\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\signature{Ivan Evdokimov}

\begin{document}

\begin{letter}{Hiring Committee\\
Rosalind Franklin Institute}

\opening{Dear Hiring Committee,}

I am writing to apply for the Research Software Engineer position at the Rosalind Franklin Institute. I hold a PhD in Computational Finance and have over four years of experience developing scientific software, machine learning systems, and high-performance computing solutions. I am motivated by the Franklin’s mission to advance technologies for the life sciences through interdisciplinary collaboration.

In my current role at the University of Essex, I design and deploy reproducible machine learning pipelines and CI/CD workflows that support rapid experimentation and reliable deployment. I have developed automated validation frameworks for AI-generated code, improving robustness while significantly reducing manual review effort. This has strengthened my ability to translate evolving research requirements into scalable software systems.

Previously, at the UK Data Service, I developed machine learning models for sensitive social science datasets and designed cloud-based data pipelines to enable scalable, reproducible workflows. I also optimised statistical algorithms by porting them from R to C++, achieving an 11-fold performance improvement. This work involved close collaboration with domain experts to ensure solutions were both technically sound and aligned with research requirements.

During my PhD, I developed a PyTorch-based framework for Bayesian model averaging, contributing to peer-reviewed research and open-source software. I also built and optimised large-scale simulation models in C++ and collaborated internationally on computational research projects.

I am particularly interested in contributing to the Franklin’s Advanced Research Computing platform, supporting scalable cloud and HPC solutions, and enabling data-intensive research through robust software and best practices.

Thank you for your consideration. I would welcome the opportunity to contribute to the Franklin’s mission.

\closing{Yours sincerely,}

\end{letter}

\end{document}
