\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}  % Style options: 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}     % Color options: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

\usepackage[scale=0.75]{geometry}

% Personal Information
\name{Ivan}{Evdokimov}
\email{vanyaevdokimov14@gmail.com}
\phone[*]{+44 7586 774312}

% Custom Variables
\newcommand{\positionname}{Graduate AI \& Software Engineer}
\newcommand{\companyfull}{~Cortex Reply~}
\newcommand{\companyshort}{Cortex Reply}

\begin{document}

% Cover Letter Header
% \recipient{Hiring Manager}{\companyfull \\ 17 Marble Street, \\ Manchester, M2 3AW}
\recipient{Hiring Manager}{}
\date{\today}
\opening{Dear Hiring Manager,}
\closing{Kind regards,}

\makelettertitle

I am writing to express my enthusiasm for the Graduate AI \& Software Engineer position at \companyshort, starting January 2026. With a PhD in Computer Science from the University of Essex and hands-on experience building machine learning and software systems on AWS, I am eager to contribute my technical skills and passion for applied AI to your consulting and engineering teams.

 In my current role as an AI Software Engineer at the UK Data Service, I have developed and deployed end-to-end ML classification systems in scikit-learn and PyTorch, leveraging Docker for containerization and AWS for cloud scalability. I also integrated fine-tuned LLMs using Hugging Face Transformers to automate metadata classification workflows. These experiences have strengthened my ability to deliver production-ready AI solutions that balance technical performance with maintainability and security.

My academic and research background has further deepened my expertise in machine learning, data engineering, and statistical modeling. During my PhD, I developed a Transfer Learning-based Bayesian Averaging framework for predictive modeling in financial systems, which was adopted by other open-source projects. Alongside this, I have mentored students in Reinforcement Learning, GANs, and Software Engineering practices, and gained exposure to collaborative, agile-driven research environments—skills that directly align with Cortex Reply’s multidisciplinary and client-facing approach.

What excites me most about this opportunity is \companyshort’s commitment to developing consultants who bridge AI innovation and cloud engineering. The structured graduate program and certification pathway in AWS and Terraform perfectly match my goal of becoming a technically versatile consultant who can architect, deploy, and explain AI-driven solutions across industries. I am particularly drawn to the chance to work with leading experts in the Applied AI Business Unit, where I can apply my technical knowledge while continuously growing in consulting and cloud disciplines.

I would be delighted to discuss how my experience and interests align with \companyshort’s mission to deliver cutting-edge AI and cloud solutions. Thank you for considering my application — I look forward to the opportunity to contribute to your team.

\vspace{0.25cm}
Kind regards,

Ivan Evdokimov
\end{document}


